Quantitative Auditing of AI Fairness with Differentially Private Synthetic Data

### 2024-12-19 paper/paper.tex
Rewrite conclusion

Auditing AI systems with real data can be dangerous. We proffer a new approach that leverages differentially private synthetic data. The proposed framework under such privacy guarantees offers a refuge from the vulnerabilities of using real data.

Despite the fact that some measures' definitions betray the inherent imperfection of synthetic data, the metrics results remain generally consistent with the original data. Empirical trials across multiple real-world datasets and real-world models reveal that synthetic data derived from real data sufficiently maintains the fairness properties to serve as instruments of audit.

Auditors are, thus, in our new framework, equipped with a new tool that tempers risk at the cost of nuance. Synthetic data, imperfect as it is, emerges as a pragmatic ally, preserving enough fairness properties for auditing utility without sacrificing the sanctuary of privacy.

>>>>

Auditing AI systems with real data can be dangerous. We propose a new approach that leverages differentially private synthetic data. The proposed framework, with its strong privacy guarantees, provides a safe alternative to the risks of using real data.

Despite the inherent imperfection of synthetic data for some measures, the metrics results remain generally consistent with the original data. Experiments on multiple real-world datasets and real-world models reveal that synthetic data derived from real data maintains fairness properties.

While synthetic data is not perfect, it serves as a practical tool for auditing AI fairness. Our framework provides an effective way to audit AI systems without compromising privacy. Future work includes applications on larger datasets to validate scalability and explorations of other means of privacy preservation in AI auditing.
